Simulation Study Document: Same Mean Same Variance

### 2021-09-30 Simulation Study Document with same mean same var.Rmd
changes to the doc

---
title: "Simulation Study Document V4"
author: "Paul Harmon"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

@@

  xTSNE <- MultiPermanova(yes_structure_final[,1:10], maptype = "tSNE")
  results_list[[j]] <- xTSNE

>>>>

---
title: "Simulation Study Document: Same Mean Same Variance"
author: "Paul Harmon"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

@@

  xTSNE <- MultiPermanova(yes_structure_final[,1:10], maptype = "tSNE", perp_val = 20)
  results_list[[j]] <- xTSNE
